\typeout{ ====================================================================}
\typeout{ this is file letter.tex, created at 13-Nov-2014               }
\typeout{ maintained by Gustavo Rabello dos Anjos                             }
\typeout{ e-mail: gustavo.rabello@gmail.com                                   }
\typeout{ ====================================================================}


\documentclass{letter}
\usepackage{hyperref}
\signature{Prof. Gustavo Anjos}
\address{GESAR/UERJ \\
         Rua Fonseca Teles, 121 \\ 
		 S\~ao Crist\'ov\~ao \\ 
		 Rio de Janeiro -- Brazil}


\begin{document}

\begin{letter}{University of California -- Los Angeles \\
               Graduate Division
}
\opening{Dear Sir or Madam:}

I am writing this letter for Mr. Eduardo Vitral Freigedo Rodrigues
regarding his work under my orientation at the GESAR group. I confirm
that Eduardo has been working in the GESAR lab as a master student for
about 3 months period and he plans to finish his master dissertation in
July, 2015. He was granted with a master student scholarship which will
completly cover his studies at the State University of Rio de
Janeiro.

I met Mr. Eduardo Vitral while he was an undergraduate student at the
Metalurgy and Materials Engineering Department in the Federal University
of Rio de Janeiro -- UERJ/COPPE, in 2012. He is an outstanding student,
showing excellent intellectual skills, great interest in research, and
ranking first in his class.

Currently, Mr. Eduardo Vitral is following specific courses to improve
his knowledge in material science and numerical methods. He has
successfully accomplished a challenging course of Finite Element Method,
... and he is following ....

He speaks English and French very well, he is articulate, and he is a
diligent and motivated person. He has shown good writing skils while
preparing presentations, reports and manuscripts, and he also plans to
writing his thesis in English, although not mandatory at the University
of Rio de Janeiro.

In summary, I wish to give my very, very strong recommendation to Mr.
Eduardo Vitral for his future career in research. I have absolutely no
doubt that he will excel and that we will hear much more from him in the
future.


\closing{Yours Faithfully,}

\end{letter}
\end{document}


\typeout{ ****************** End of file letter.tex ****************** }

